Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-03-18 thesis/chapters/ch_introduction.tex
reformatting hydro equations and removing uneeded comment

\subsection{Hydrodynamics}
\textit{(This will be a sub-section of something, but putting here for now as placeholder).}

Astrophysical hydrodynamics simulations are first distinguished by the numerical methods employed to solve the Euler equations that describe the time ($t$) evolution of the energy density ($E$), density ($\rho$), pressure ($p$), and peculiar velocity ($\bm{v}$) of a fluid:
\begin{equation}
  \frac{\delta \rho}{\delta t} + \nabla \cdot \left(\rho \bm{v}\right)  = 0,\\
  \frac{\delta \rho \bm{v}}{\delta t} + \nabla \cdot \left(\rho \bm{v}\bm{v} + \bm{I}p \right) = 0,\\
  \frac{\delta E}{\delta t} + \nabla \cdot \left[\left(E +p\right)\bm{v}\right] = 0.
\end{equation}

@@

In galaxy-scale hydrodynamics, star formation is typically treated as a process that occurs by a sub-grid model, with an assumed rate and assumed efficiency, in fluid elements that surpass a variety of threshold conditions. Usually, simulators set these thresholds to fully encompass gas whose Jeans-length (and thus dynamical behavior) becomes unresolved according to the widely-used \cite{Truelove1997} criterion. Often, this means a simple mass or number density threshold, on top of which simulators can also require that the local gas cells be in a converging flow ($\div \bm{v} < 0$), that gas surpass some virial threshold \citep[e.g.][]{}, or that gas also meet a minimum $H_2$ mass fraction \citep[e.g.][]{}. One a fluid element is flagged as star forming, simulators have a few options to choose from in how to determine what fraction and with what rate that mass is converted into stars. Briefly, some form of the following equation is usually adopted,
\begin{equation}
\label{intro:eq:sfr}
 \rm{SFR} \propto 
\end{equation}
,. Some works adopt modifications of this simple perscription, with varying star formation efficiency ($\eta$) (refs), or XXXX. Others, for application in high-resolution simulations where the mass of stars that would form in a single timestep ($dt \times \rm{SFR}$) is far less than a single star particle mass, allow stars to form out of star forming fluid elements stochastically \citep[e.g.][]{Goldbaum2015}.

>>>>

\subsection{Hydrodynamics}
Astrophysical hydrodynamics simulations are first distinguished by the numerical methods employed to solve the Euler equations that describe the time ($t$) evolution of the energy density ($E$), density ($\rho$), pressure ($p$), and peculiar velocity ($\bm{v}$) of a fluid:
\begin{align}
  \frac{\delta \rho}{\delta t} + \nabla \cdot \left(\rho \bm{v}\right)  &= 0,\\
  \frac{\delta \rho \bm{v}}{\delta t} + \nabla \cdot \left(\rho \bm{v}\bm{v} + \bm{I}p \right) &= 0,\\
  \frac{\delta E}{\delta t} + \nabla \cdot \left[\left(E +p\right)\bm{v}\right] &= 0.
\end{align}

@@

In galaxy-scale hydrodynamics, star formation is typically treated as a process that occurs by a sub-grid model, with an assumed rate and assumed efficiency, in fluid elements that surpass a variety of threshold conditions. Usually, simulators set these thresholds to fully encompass gas whose Jeans-length (and thus dynamical behavior) becomes unresolved according to the widely-used \cite{Truelove1997} criterion. Often, this means a simple mass or number density threshold, on top of which simulators can also require that the local gas cells be in a converging flow ($\nabla \bm{v} < 0$), that gas surpass some virial threshold (describing how bound a cloud may be)
%cite?, 
or that gas meet a minimum $H_2$ mass fraction
%\citep[e.g.][]{}
. Once a fluid element is flagged as star forming, simulators have a few options to choose from in how to determine what fraction and with what rate that mass is converted into stars. Briefly, some form of the following equation is usually adopted,
\begin{equation}
\label{intro:eq:sfr}
 \rm{SFR} \propto 
\end{equation}
,. Some works adopt modifications of this simple perscription, with varying star formation efficiency ($\eta$) (refs), or XXXX. Others, for application in high-resolution simulations where the mass of stars that would form in a single timestep ($dt \times \rm{SFR}$) is far less than a single star particle mass, allow stars to form out of star forming fluid elements stochastically \citep[e.g.][]{Goldbaum2015}.
